Catchy Title Goes Here

### 2018-06-18 Paper/paper.tex
updated results section in paper, added figures

\subsection{Model Comparison}
For the real data from the DRC, we wish to determine which provinces warrant the more complicated seroprevalence model from Sec.~\ref{subsec:CompetingRates} that includes a constant in addition to the Weibull function, and which are described sufficiently by a constant force of infection alone. To do this, we calculate the Bayes factor between the two models, which, given that our prior belief in the two models is equal, is simply the ratio of the evidence for each of the models. The evidence is the fully marginalized likelihood (FML), and can often be quite difficult to calculate accurately. Luckily for us, the two models in question are nested - we recover the constant-only model when $\alpha = 1.0$ -  and so we can use a technique called the Savage-Dickey density ratio.

@@

We generate these distributions for each province independently using Markov chain Monte Carlo techniques, described in the next section, and find that only three provinces are adequately described by the constant force of infection model: Bandundu, Kasai Occidental, and Maniema. The rest of the provinces require the more complicated Weibull plus constant model. For all of the results presented in Sec.~\ref{sec:Results}, we use these models as noted here for each of the provinces.

@@

\subsection{Comparing Data and Inference \label{subsec:Comp}}
A standard approach for interpreting the results of Bayesian inference would be to inspect the posterior distributions for the model parameters. But the parameters of our model are not, in themselves, particularly interesting - it is the inferred seroprevalence, case distribution, and vaccination probability that we wish to compare with the data. To do this, we generate the posteriors on $\{\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v\}$ as described, and then draw from these posteriors to generate the seroprevalence, case, and vaccination curves as laid out in Sec.~\ref{subsec:CompetingRates}. Because the vaccine efficacy, $\gamma$, is of interest on its own, we also examine the posterior distributions on $\gamma$ in detail.

@@

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vh, and $\gamma$ (vaccine efficacy), and examine the results.

Figure~\ref{fig:simplots} shows the injected (dashed lines) and recovered (solid (purple or orange) lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy of $\gamma = 0.9$ (orange) and $\gamma = 0.6$ (indigo). The top panel shows the force of infection, and it is very clear from this panel that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in Figure~\ref{fig:simplots}.

@@

This figure shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top panel is generated by analyzing all three datasets, and the bottom panel using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top panel we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is worth noting that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

The bottom panel in this same Figure shows the inferred values for vaccine efficacy using only case and vaccination data - i.e. leaving out the serology data from the analysis. For the higher levels of $\gamma$, the results are dominated by the prior. For the lower values, we are again biased quite low, but also again recover the correct ranking of vaccine efficacy.

Finally, we wish to explore the recovered fits to the true data when analyzing only the case and vaccination data. These results are shown in Fig.~\ref{fig:svcsimdata}. Here, we show the recovered (lines) vaccination prevalence, seroprevalence, and case distribution for simulated data with vaccine efficacy of $\gamma = 0.6$ (indigo) and $\gamma = 0.9$ (orange). The true values for each of these are shown as points. We can see that the case and vaccination data are fit well by the recovered model parameters - unsurprising, given that this is the data that was used in the fitting analysis. The seroprevalence data is also fit well in the case of $\gamma = 0.9$, which recall is one of the values for which the posterior on $\gamma$ is essentially the same as the prior, which includes a lot of weight at the true value. The seroprevalence when $\gamma = 0.6$ is much more biased, although it still follows some of the qualitative features of the true data. Thus for values of vaccine efficacy that are near to the peak of our prior distribution, the seroprevalence inferred using only vaccination and case data is quite accurate. For lower vaccine efficacies, though, seroprevalence data is almost certainly needed to achieve an accurate picture.

\subsection{Application to DRC Data \label{subsec:DRC}}
\begin{figure*}
\includegraphics[width=0.85\textwidth,angle=0]{figures/SeroPlots-crop.pdf}
\caption{caption\label{fig:sero}}
\end{figure*}
\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/VaccFOIveff-crop.pdf}
\caption{caption\label{fig:foivaccveff}}
\end{figure*}
\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/RiskRank-crop.pdf}
\caption{caption\label{fig:riskrank}}
\end{figure}

>>>>

\subsection{Model Comparison\label{subsec:BF}}
For the real data from the DRC, we wish to determine which provinces warrant the more complicated seroprevalence model from Sec.~\ref{subsec:CompetingRates} that includes a constant in addition to the Weibull function, and which are described sufficiently by a constant force of infection alone. To do this, we calculate the Bayes factor between the two models, which, given that our prior belief in the two models is equal, is simply the ratio of the evidence for each of the models. The evidence is the fully marginalized likelihood (FML), and can often be quite difficult to calculate accurately. Luckily for us, the two models in question are nested - we recover the constant-only model when $\alpha = 1.0$ -  and so we can use a technique called the Savage-Dickey density ratio.

@@

We generate these distributions for each province independently using Markov chain Monte Carlo techniques, described in the next section, and find that only three provinces are adequately described by the constant force of infection model:  Bas Congo, Kasai Occidental, Kasai Orientale, and Maniema. The rest of the provinces require the more complicated Weibull plus constant model. For all of the results presented in Sec.~\ref{sec:Results}, we use these models as noted here for each of the provinces, except for Equateur. In Equateur, the more complicated model was preferred when fitting all three datasets, but the constant only model was preferred when fitting only case and vaccination data, and so these models were used accordingly.

@@

\subsection{Comparing Data and Inference \label{subsec:Comp}}
A standard approach for interpreting the results of Bayesian inference would be inspecting the posterior distributions for the model parameters. But the parameters of our model are not, in themselves, particularly interesting - it is the inferred seroprevalence, case distribution, and vaccination probability that we wish to compare with the data. To do this, we generate the posteriors on $\{\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v\}$ as described, and then draw from these posteriors to generate the seroprevalence, case, and vaccination curves as laid out in Sec.~\ref{subsec:CompetingRates}. Because the vaccine efficacy, $\gamma$, is of interest on its own, we also examine the posterior distributions for this parameter in detail.

@@

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vaccination hazard, and $\gamma$ (vaccine efficacy), and examine the results.

Figure~\ref{fig:simplots} shows the results from this analysis. In the top right panel, we show the injected (dashed lines) and recovered (solid lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy ranging between $\gamma = 0.9$  and $\gamma = 0.6$. The top graph in this panel shows the force of infection, and it is very clear that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in the top left panel of this same figure.

@@

This panel shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top plot is generated by analyzing all three datasets, and the bottom plot using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is important to note that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

The bottom plot in this same panel shows the inferred values for vaccine efficacy using only case and vaccination data - i.e. leaving out the serology data from the analysis. For the higher levels of $\gamma$, the results are dominated by the prior. For the lower values, the recovered values are again biased quite low, but also again recover the correct ranking of vaccine efficacy.

Finally, we wish to explore the recovered fits to the true data when analyzing all of the simulated datasets. These results are shown in the bottom panel of Fig.~\ref{fig:simplots}. Here, we show the recovered (lines) seroprevalence, vaccination probability, and case distribution for simulated data with vaccine efficacy of $\gamma = 0.6$ (indigo) and $\gamma = 0.9$ (orange). The true values for each of these are shown as points. We can see that the injected data is recovered well with our model, even though the foi and vaccination hazard are not fit particularly well themselves. This is because the data are a function of the \emph{integrated} foi and vaccination hazard, which allows for some ambiguity in the details of the functions themselves.

\subsection{Application to DRC Data \label{subsec:DRC}}
We now turn our attention the the results of our analyses when using the real data from the DRC. As discussed in Section~\ref{subsec:BF}, we first determined which model for foi was preferred for each of the eleven provinces we used for our geographical units. We found that when all of the data was included, the only provinces that were better-described by the simple, constant-only model were Bas-Congo, Kasai Occidental, Kasai Orientale, and Maniema. When we looked at the case and vaccination data only, Equateur was also better-described by this model, and when we analyzed only the seroprevalence data, the analysis for all provinces preferred this model.

\begin{figure*}
\includegraphics[width=0.85\textwidth,angle=0]{figures/SeroPlots-crop.pdf}
\caption{\label{fig:sero} Left panel: color coding of locations used in our analysis. The data was split into the 11 provinces in existence between 1997 and 2015. The map shows these provinces in different colors, as well as the current administrative boundaries as black lines. The colors on this map correspond to the colors used for each province in all figures in this section. Right panel: seroprevalence data (points) and inferred values up to 25 years. The solid line shows the mean of the posterior distribution for the inferred seroprevalence using all three datasets, while the dashed lines show the full range of the posterior distribution generated using only vaccination and case data. The provinces before the blank space were fit using the Weibull plus constant model for force of infection, while those after (starting with Bas Congo) were fit using only a constant. For the provinces in which seroprevalence data makes a difference in the inferred values, the inferred curve is typically lower than that generated using only vaccination and case data. This is especially pronounced in Sud Kivu.}
\end{figure*}

The left panel of Fig.~\ref{fig:sero} the color-coded provinces. We use these colors throughout this section to show the results from individual provinces. The right panel shows the recovered seroprevalence data (right panel) for all 11 provinces, using all three datasets (solid line) and the vaccination and case data only (dashed lines). The solid line is the mean of the posterior distribution generated using all three datasets, while the dashed lines show the full range of the posterior for the vaccination/case data analysis. We see that, in general, the seroprevalence data leads to a \emph{lower} estimate of seroprevalence in the population than the case and vaccination data alone. This is because the prior on vaccine effectiveness is peaked around $0.85$ - that is, when a study participant reports that they or their child is vaccinated, we give an $85\%$ probability that not only is the recollection correct, but that the vaccine produced immunity. Without seroprevalence data, there is not enough information in the datasets to pull the value for $\gamma$ away from this peak, and so we overestimate the immunity in the population. This is particularly noticeable in the results for Sud Kivu. The only province for which this is not the case is Maniema, but looking at the seroprevalence data for Maniema reveals many age groups for which $100\%$ of the population are seropositive. This suggests either a small number of participants, which could be taken into account in future analyses, or something that went wrong with the data reporting.

\begin{figure*}
\includegraphics[width=\textwidth,angle=0]{figures/VacFOIveff-crop.pdf}
\caption{\label{fig:foivaccveff} Left panel: Vaccination hazard (solid lines, right y-axis) and vaccination coverage (dashed lines, left y-axis) recovered using all three sets of data from all 11 provinces, generated from a set of posterior samples. For most provinces, the vaccination hazard is tightly peaked near one year, as expected. Middle panel: The recovered force of infection using all data (solid curve) and only vaccination and case data (dashed curves). As in Figure~\ref{fig:sero}, the solid curve is the mean of the posterior distribution, and the provinces before the blank space were fit using the Weibull plus constant model while those after were fit using the constant-only model for force of infection. In most cases, the inclusion of the serology data did not make a large difference in the inferred force of infection. Right panel: recovered value for vaccine efficacy ($\pm 1\sigma$) from analyses using all three data sets for each province. Because of our results from the simulated data, we do not expect that these values to reflect the true vaccine efficacy (in general, they are probably biased low), but we \emph{do} expect that the ranking of provinces by vaccine efficacy is correct.}
\end{figure*}

In the next figure, Fig.~\ref{fig:foivaccveff}, we examine the vaccination hazard and probability, the force of infection, and the vaccine efficacy for each of the eleven provinces, inferred using all three datasets. The left panel shows the vaccination data as points, the vaccination hazard as solid lines, and the vaccination probability as dashed lines. All curves are generated from samples drawn from the posterior distributions of the model parameters. For almost all of the provinces, the vaccination hazard is peaked tightly around approximately one year in age, as expected. The height of the vacc. hazard corresponds closely to the final level of vaccination probability - higher vaccination hazard means a higher probability of getting vaccinated. The only province that does not follow this pattern is Bas Congo, for which there is evidence for a vaccination hazard with non-negligible weight at higher ages. That is, the probability of being vaccinated is still increasing at the right edge of this graph, which corresponds to five years old.

The next (middle) panel in Fig.~\ref{fig:foivaccveff} shows the force of infection recovered for each province using all data (solid) and vaccionation/case data (dashed). For all provinces except Equateur, the force of infection is either Weibull plus constant (first seven cells), or constant-only (final four cells) for both datasets. In Equateur, the simpler model is used when vaccination/case data only are used. We see here that all provinces have a non-zero force of infection at higher ages.

The final (right) panel in Fig.~\ref{fig:foivaccveff} shows the mean value and uncertainty for vaccine efficacy ($\bar{\gamma} \pm \sigma$) for all eleven provinces, with the same color-coding as has been used throughout this section. As expected from the serology results, Sud Kivu has the lowest vaccine efficacy. Because of our results using the simulated data, we believe that the ordering of provinces by $\gamma$ is correct - but we do not believe that the actual values should be taken seriously. From that analysis, we suspect that the recovered values are likely lower than the true values.

\begin{figure}
\includegraphics[width=\columnwidth,angle=0]{figures/RiskRank-crop.pdf}
\caption{\label{fig:riskrank} Force of infection integrated to age ten (`risk' )for all eleven provinces, color coded as indicated in Figure~\ref{fig:sero}, calculated using the inferred foi from only serology data (left-most point), case and vaccination data (middle point), and all three datasets. Both the ranking of provinces by risk and the overall values change dramatically between the serology-only and the other two points, but the difference between vaccination plus case and all three data sets is minimal. The maps show the risk in all provinces, with yellow being high risk and dark blue being low risk. }
\end{figure}

Finally, in Fig.~\ref{fig:riskrank}, we assess what we call the `risk' inferred for with each province, which we define as
\begin{equation}
r = \int_0^{10} \mathrm{foi}(a) da,
\end{equation}
 or the force of infection integrated from 0 to $10$ years. We calculate the foi using serology data only (left-most point), case and vaccination data only (middle point), and all three datasets (right-most point), and show the integrated values in Fig.~\ref{fig:riskrank}. The provinces are color-coded as throughout this section, and a dashed line is drawn to guide the eye between the results for different datasets. Below the points, we show maps of the DRC with each province colored according to the risk level, with dark blue being lowest risk and yellow highest. The most obvious conclusion from this plot is that the inclusion of case and vaccination data leads us to drastically increase our assessment of risk in many provinces. Interestingly, the inclusion of serology data does not make a significant difference in the calculated risk. The information from serology data seems to be most useful for inferring vaccine efficacy, rather than force of infection.
